Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-13 inspiral_svd.tex
Changing optical to EM
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1000 ccdd05d5-56c1-461a-bf98-85f6876523b4
Added DCC version number
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1028 ccdd05d5-56c1-461a-bf98-85f6876523b4
Updated DCC version
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1053 ccdd05d5-56c1-461a-bf98-85f6876523b4
Incremented DCC version to 17
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1060 ccdd05d5-56c1-461a-bf98-85f6876523b4
Reworded acknowledgements
git-svn-id:

\LIGO\ was constructed by the California Institute of Technology and
Massachusetts Institute of Technology with funding from the National Science
Foundation and operates under cooperative agreement
\textsc{phy}-\oldstylenums{0107417}.  CH would like to thank Ilya Mandel for
many discussions about rate estimates and the prospects of early detection.  CH
would also like to thank Patrick Brady for countless fruitful conversations
about low latency analysis methods.  NF would like to thank Alessandra Corsi
for illuminating discussions on astronomical motivations.  DK was supported
from the Max Planck Gesellschaft. This research is supported by the National
Science Foundation through a Graduate Research Fellowship to LS and by a
fellowship from The Perimeter Institute for Theoretical Physics to CH.

This paper has \LIGO\ Document Number \LIGO-\textsc{p}\oldstylenums{0900004}.

>>>>

\LIGO\ was constructed by the California Institute of Technology and
Massachusetts Institute of Technology with funding from the National Science
Foundation and operates under cooperative agreement
\textsc{phy}-\oldstylenums{0107417}.  CH would like to thank Ilya Mandel for
many discussions about rate estimates and the prospects of early detection.  CH
would also like to thank Patrick Brady for countless fruitful conversations
about low latency analysis methods.  NF would like to thank Alessandra Corsi
for illuminating discussions on astronomical motivations.  This research is
supported by the National Science Foundation through a Graduate Research
Fellowship to LS and by the Perimeter Institute for Theoretical Physics
through a fellowship to CH. DK is supported from the Max Planck Gesellschaft.

This paper has \LIGO\ Document Number \LIGO-\textsc{p}\oldstylenums{0900004}-v\oldstylenums{17}.
